# Exploratory data analysis

```{r, echo = FALSE, message = FALSE}
source(here::here("scripts/setup.R"))
```

# Basics informations: 

* This dataset contains 1000 observation & 31 variables.
* In its raw format, we can observe that all the variables are of "integer" formats.
* In this example we are showing variables that are in the incorrect formats
```{r, echo = FALSE, message = FALSE}
str(GermanCredit_raw[c("CHK_ACCT", "HISTORY", "NEW_CAR", "USED_CAR")])
```
After transformation, of those variables to match their desire format, we get a data set with the rights formats:
```{r, echo = FALSE, message = FALSE}
str(GermanCredit[c("CHK_ACCT", "HISTORY", "NEW_CAR", "USED_CAR")])
```

DfSummary tables:

From the summary we can observe the following information:

* The target variable "RESPONSE" is unevenly distributed, meaning that we will need to sub-sample our data set while modeling it. 
* We can observe that "NUM_CREDITS"; "EDUCATION"; "GUARANTOR"; "JOB" are categorial variables with more than two factors levels, however their distribution are uneven, thus in each case a factor level is close to unsignificance in term of proportion. 
* Finally the dfSummary table shows us that none of the numerical variable follows a Gaussian distribution, thereby we will need to scale them. For this case, we will use a min/max scaling.
```{r, echo = FALSE, message = FALSE}
view(dfSummary(GermanCredit, style="grid",plain.ascii = FALSE, tmp.img.dir = "/tmp"))
```

Before exploring this dataset, we want to ask ourself the following question: Is the target variable balanced ?
It turns out that this is not the case, thereby prior to our modelization, we will need to subsample this data set.
```{r, echo = FALSE, message = FALSE}
table(GermanCredit$RESPONSE)
```


Boxplot informations for numerical value in regard to the target "RESPONSE":
* Except for the variable "INSTALL_RATE" & "Duration" the rest of the variables seem to have close median results.

```{r, echo = FALSE, message = FALSE}
lblue <- "#6699CC"
par(mfrow = c(2, 3))
boxplot(DURATION ~ RESPONSE, data = GermanCredit, xlab = "Duration", notch = T,
        varwidth = T, col = lblue)
boxplot(AMOUNT ~ RESPONSE, data = GermanCredit, xlab = "Amount", varwidth = T, col = lblue)
boxplot(INSTALL_RATE ~ RESPONSE, data = GermanCredit, xlab = "Install_rate", varwidth = T, col = lblue)
boxplot(AGE ~ RESPONSE, data = GermanCredit, xlab = "Age", varwidth = T, col = lblue)
boxplot(NUM_CREDITS ~ RESPONSE, data = GermanCredit, xlab = "Num_credit", varwidth = T, col = lblue)
```

# Correlation

We now desire to take a glance a the correlation matrix between the numerical variables.
From this plot we understand the following information:

* AMOUNT & DURATION have the highest positive correlation: 62.5%
* AGE & NUM_CREDIT constitute the second highest positive correlation however the value is insignficant compare to the prior: 14.26%

On the other side of the spectrum for negative correlation:

* AMOUNT &  INSTALL_RATE are the most signfiicant with a value of: -27.13%

```{r, echo = FALSE, message = FALSE}
corr_matrix <-cor(x = as.matrix(GermanCredit_num), method = "pearson", use = "pairwise.complete.obs")
melted_corr_matrix <- melt(corr_matrix, na.rm = TRUE)
ggplot(data = melted_corr_matrix, aes(x = Var1, y = Var2, fill = value))+
  geom_tile()+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white",
                       midpoint = 0, limit = c(-1,1), space = "Lab",
                       name = "Pearson\nCorrelation")+
  theme_minimal()+
  theme(axis.text = element_text(angle = 45, vjust = 1,
                                 size = 12, hjust = 1))+
  coord_fixed()
```

Another way of showing the correaltion is through the following plot:
```{r, echo = FALSE, message = FALSE, warning=FALSE}

x<-inspect_cor(GermanCredit[,-31])
show_plot(x, col_palette=4)
```


We then wish to look at the correlation between the categorical variables. 
For this particular plot, it is important to note that the target variable(RESPONSE) is include while for the numerical correlation matrix it was not the case. 
From this factor matrix, we get insight on the following information for the relationship with RESPONSE:

* The highest positive correlation is with CHK_ACCT3: 32%
* The highest negative correlation is with CHK_ACCT0: -26%

This information is interesting in the sens that:

* CHK_ACCT0: < 0 DM in a checking account 
* CHK_ACCT3: No checking account

Thus for the bank an applicant without a checking is more interesting than a client with more than 200DM. However, this might become detrimental if the bank can not convince the applicant to open a checking account, in which case it ends up with the negative effect found with CHK_ACCT0.
Finally, we are witnessing an intriguing positive relationship with STATUS:

* HISTORY4: ~20%

The reason why we consider this correlation weird is because this variables corresponds to a situation where an applicant is in a "critical" state in the bank eyes. Meaning, that the applicant has a clear pattern of being late to pay off. 

```{r, echo = FALSE, message = FALSE}
model.matrix(~0+., data=GermanCredit_fac) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(show.diag =T, type="lower", lab=TRUE, lab_size=0.8)+
  theme(axis.text.x = element_text(size = 4),
        axis.text.y = element_text(size = 5))
```

# Distribution

We now wish to dig deeper into potential relationship among our variables by theme in term of distribution over our target REPONSE.
Our first interest concerns the marital status of the applicant:

* If a man is not divorced or is, there's still a higher chance for him to have a bad credit score.
* If a man is not single, the probability that he'll have a bad /good credit score is pretty close. However, if he's single, then there is a higher chance that he'll have a good credit score
* If a man is neither married nor widower, the result would be close to those with a non-divorced man. However, should he be married or widower, then there would be a small but still higher chance for him to have a good credit score.

```{r, echo = FALSE, message = FALSE}
GermanCredit %>% select(MALE_DIV, MALE_SINGLE, MALE_MAR_or_WID, RESPONSE) %>%
  ggpairs()
```

We now want to look a the purpose of the credit: It is interesting to see that no matter the purpose of a credit taken, if the binary response is "yes" the chance for a good credit will be higher. Nonetheless, it is also we also to see that the chance of having a applicant with a bad credit score is still higher.
```{r, echo = FALSE, message = FALSE}
GermanCredit %>% select(NEW_CAR, USED_CAR, FURNITURE, RADIO.TV, EDUCATION, RETRAINING, RESPONSE) %>%
  ggpairs(proportions = "auto") +
  theme(axis.text.y  = element_text(size = 4),
        axis.text.y.right = element_text(size = 1))
```
Looking at the distribution for past history, we get the following information:

* What we found out with the factor matrix is confirmed for CHK_ACCT
* There is a highest probability of having an applicant with a  RESPONSE of type 1 (meaning that he has a good credit score) if his number of credit is of level 1.
* While we found out that REPONSE had a positive correlation with HISTORY4, we can see that in term of distribution, there is a higher chance for an applicant to have a good score if its level is of 2 (Existing credit to be paid, always on time).
* Finally, an individual with no other installment is more incline of having a good credit score.

```{r, echo = FALSE, message = FALSE}
GermanCredit %>% select(CHK_ACCT, NUM_CREDITS, HISTORY, INSTALL_RATE, OTHER_INSTALL, RESPONSE) %>%
  ggpairs()
```

Concerning the guarantee:

* It seems that the bank is better off if the applicant has no co-applicant which is a surprise.
* The same applies for guarantor.
* The behavior of the distribution for PRESENT_RESIDENT is closely identical for either RESPONSE.

Finally, for SAV_ACCT the bank may want to invest for level 1 & 4:

* Level 1: < 100 DM in a saving account
* Level 4: unknown / no saving account. 
```{r, echo = FALSE, message = FALSE}
GermanCredit %>% select(CO.APPLICANT, GUARANTOR, PRESENT_RESIDENT,SAV_ACCT, RESPONSE) %>%
  ggpairs()
```

In regard of the real estate:

In each case, except for OWN_RES the proportion of binary response 0 is higher. Nonetheless the target variables RESPONSE always has a higher probability of showing 1.
This of course, is explained by the unbalanced data set that we have. 
```{r, echo = FALSE, message = FALSE}
GermanCredit %>% select(REAL_ESTATE, OWN_RES, PROP_UNKN_NONE, RENT, RESPONSE) %>%
  ggpairs()
```

Looking at the employment & dependency:

* It is interesting to see that there seems to be  a higher chance for a good credit score if the applicant has been employed between 4-7 years.
* The same goes for applicant who's category under job is "un-skilled - resident" than for the other.
* For the dependent category, there's a higher chance for an applicant to have a good credit score if the number of liable individual is close to 1.
```{r, echo = FALSE, message = FALSE}
GermanCredit %>% select(EMPLOYMENT, JOB, NUM_DEPENDENTS, RESPONSE) %>%
  ggpairs()
```

Concerning foreigners applicant:

For this category we can see that proportion of bad credit score is way more significant if the applicant is foreigner. However, the probability that he'll have a good credit score is lower if he's not foreigner which is pretty interesting
```{r, echo = FALSE, message = FALSE}
GermanCredit %>% select(FOREIGN, RESPONSE) %>%
  ggpairs(proportions = "auto")
```

In regard of phone: 

We can see that having a phone would drasticly increase the probability that the applicant would have a good credit score
```{r, echo = FALSE, message = FALSE}
GermanCredit %>% select(TELEPHONE,RESPONSE) %>%
  ggpairs(proportions = "auto")
```



